---
title: "FR Covid-19 Survey Report"
date: "`r Sys.Date()`"
output: pdf_document
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
params:
  dataout: "data/"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)
library(tidyverse)
library(dotenv)
library(REDCapR)
library(lubridate)
library(kableExtra)
library(skimr)
source("functions.R")
```

```{r}
data_dictionary <- redcap_metadata_read(redcap_uri = Sys.getenv("URI"),
                     token = Sys.getenv("TOKEN"))$data

records <- get_records() 

write.csv(records, paste0(params$dataout, "fr_redcap_data_export_", today(), ".csv"),
          row.names = F, na = "")
  
records <- records %>% 
  filter(send_survey_invites == 1) 

total_subjects <- nrow(records)

checkbox_fields <- records %>% 
  get_checkboxes() %>%  
  mutate(checkbox_value = if_else(checkbox_value == 0, "Unchecked", "Checked")) %>% 
  pivot_wider(names_from = checkbox_value, values_from = n) %>% 
  mutate_at(vars(c("Unchecked", "Checked")), ~ replace(., is.na(.), 0)) %>%  
  rowwise() %>%
  mutate(total = sum(Checked, Unchecked, na.rm = T),
         perc_unchecked = round((Unchecked/total * 100),1),
         Unchecked = paste0(Unchecked, " (", perc_unchecked,")"),
         perc_checked = round((Checked/total * 100),1),
         Checked = paste0(Checked, " (", perc_checked,")")) %>% 
  select(field_label, "Variable" = label, Checked, Unchecked)
         
radio_fields <- records %>%
  get_radio_cols() %>% 
  rename("yes" = n) 
  
radio_field_unanswered <- radio_fields %>%
    group_by(field_label) %>%  
    mutate("yes" = total_subjects - sum(yes)) %>%      
    distinct(field_label, yes, .keep_all = T) %>% 
    mutate(label = "NAs")

radio_fields_all <- radio_fields %>% 
  bind_rows(radio_field_unanswered) %>% 
  arrange(field_label) %>% 
  mutate(perc = round((yes/total_subjects * 100), 1)) %>%  
  # total should be nrow(records) for every field_label
  # group_by(field_label) %>%  
  # mutate(total = sum(yes))
  mutate("N (%)" = paste0(yes, " (", perc,")")) %>% 
  select(field_label, "Variable" = label, "N (%)")

yes_no_fields <- records %>% 
  get_yes_no_cols() %>% 
  pivot_wider(names_from = label, values_from = n) %>%  
  mutate_at(vars(c("No", "Yes")), ~ replace(., is.na(.), 0)) %>%  
  mutate("NAs" = total_subjects - (No + Yes)) %>%  
  # total shoud be nrow(records)
  # mutate(total = No + Yes + NAs )
  pivot_longer(-field_label, names_to = "label", values_to = "value") %>% 
  mutate(perc = round((value/total_subjects * 100), 1)) %>% 
  mutate("N (%)" = paste0(value, " (", perc,")")) %>% 
  select(field_label, "Variable" = label, "N (%)")
  
```

This report provides the summary statistics for the First Responder Covid 19 questionnaires for research subjects with a swab result at baseline. This report is based on a de-duplicated dataset that counts each person only once even if they submitted multiple consents and questionnaires. This report is based our first encounter with each such person wherein they received a swab or saliva result.

Table 1 provides the statistics for checkbox fields, Table 2 provides the statistics for radio and yes/no fields and Table 3 provides the statistics for numeric variables. The total number of unique subjects is `r total_subjects`.

```{r}
kable(checkbox_fields %>% select(-field_label), booktabs = T, longtable = T,
      caption = "Checkbox Fields") %>% 
  kable_styling(latex_options = "repeat_header") %>% 
  pack_rows(index = auto_index(checkbox_fields$field_label))
```

```{r}
radio_and_yes_no <- radio_fields_all %>% 
  bind_rows(yes_no_fields)

kable(radio_and_yes_no %>% select(-field_label), booktabs = T, longtable = T,
      caption = "Radio and Yes/No Fields") %>% 
  kable_styling(latex_options = "repeat_header") %>% 
  pack_rows(index = auto_index(radio_and_yes_no$field_label))
```

```{r}
numeric_cols <- records %>% 
  select("Patient Age" = patient_age, 
         "Weekly hours spent on front line with direct patient contact" = q_hours_contact_patient,   
         "Weekly hours spent on the front line with public contact" = q_hours_contact_public) %>% 
  mutate_if(is.character, parse_number) %>%   
  skim() %>% 
  mutate(complete_rate = complete_rate * 100) %>% 
  select("Variable" = skim_variable, "Complete Rate" = complete_rate,
         "Mean" = numeric.mean, "Median" = numeric.p50, "SD" = numeric.sd) %>%  
  mutate_if(is.numeric, round, 1)

```

```{r}
kable(numeric_cols, booktabs = T, caption = "Numeric Variables") %>% 
  kable_styling()
```

